### 2018-04-11 paper/background.tex
updates

\subsubsection{Structure}
% definition of CHC
A Constrained Horn Clause contains a body and a head.
%
A body consisting of a conjunction of a formula that over variables and a vector of uninterpreted predicates applied to varialbes.
%
A head can either be an uninterpreted predicates applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\QZ{make it looks nice}
\begin{defn}
  A Constrained Horn Clause is definied as follows: \\
  $\cc{chc} \Coloneqq \cc{head} \gets \cc{body}$ \\
  $\cc{head} \Coloneqq \cc{False} \mid \cc{pred}$  \\
  $\cc{body} \Coloneqq \varphi \wedge \cc{preds}$ \\
  $\cc{preds} \Coloneqq \cc{True} \mid \cc{pred} \wedge \cc{preds}$ \\
  $\cc{pred} \Coloneqq$ an uninterpreted predicate applied to variables \\
  $\varphi \Coloneqq$ a formula that all variables are vocabulary \\
\end{defn}
%
% define a body function, head function, and recursion-free
For a given constrained horn clause $C$, $\bodyof{C}$ denotes
the vector of uninterpreted predicates in the body of $C$, $\consof{C}$
denotes the formula in the body.
%
It is possible for a uninterpreted predicate shows multiple times in the
body of $C$.
%
For a given constrained horn clause $C$ that is not a query,
$\headof{c}$ denotes the uninterpreted predicates of the head of $C$.
%

%define a CHC system
A Constrained Horn Clauses system is a set of constrained horn clauses 
that it has one and only one query.
%
For a given Constrained Horn Clauses system $S$,$\predof{S}$ denotes 
the set of all uninterpreted predicates in this CHC system.

>>>>

\subsubsection{Structure}
% definition of CHC
As stated in \autoref{sec:intro} a Constrained Horn Clause is a
logical implication where the antecedent is called the body and the
consequent is called the head.
%
The body is a conjunction of a logical formula, called the fact,
and a vector of uninterpreted predicates. The fact is an arbitrary
formula in some background logic, such as linear integer arithmetic.
%
The uninterpreted predicates are applied to variables which may or may
not appear in the fact.
%
A head can be either an uninterpreted predicate applied to variables or \cc{False}.
%
A Clause where the head is \cc{False} is called query.
\begin{defn}
  CHCs can be defined structurally:
\begin{align*}
  \cc{chc} &\Coloneqq \cc{head} \gets \cc{body} \\
  \cc{head} &\Coloneqq \cc{False} \\&\mid \cc{pred}  \\
  \cc{body} &\Coloneqq \varphi \wedge \cc{preds} \\
  \cc{preds} &\Coloneqq \cc{True} \\&\mid \cc{pred} \wedge \cc{preds} \\
  \cc{pred} &\Coloneqq \textsf{an uninterpreted predicate applied to variables} \\
  \varphi &\Coloneqq \textsf{a formula that all variables are vocabulary} \\
\end{align*}
\end{defn}
%
% define a body function, head function, and recursion-free
For a given CHC $C$, $\bodyof{C}$ denotes the vector of uninterpreted
predicates in the body of $C$ and $\consof{C}$ denotes the fact in the
body.
%
It is possible for an uninterpreted predicate to apper multiple times
in the body of $C$.
%
If $C$ is not a query, then $\headof{C}$ denotes the uninterpreted
predicate in the head.
%

%define a CHC system
A CHC system is a set of CHCs where exactly one clause is a query
%
For a given CHC system $S$, $\predof{S}$ denotes the set of all
uninterpreted predicates.

### 2018-04-11 paper/fig/hierarchy.tex
updates

\scalebox{0.75}{%
\begin{tikzpicture}
\begin{scope}
  \node (top) at (0,0) {\begin{tabular}{c}All Systems\\ \textsc{Undecidable}\end{tabular}};
    \node[below = 0.5 of top] (rec) {\begin{tabular}{c}Recursion Free\\
  \textsc{co-Nexptime Complete}\end{tabular}};
  \node[below = 0.5 of rec] (dir) {\begin{tabular}{c}Directly Solvable\\ \textsc{co-NP}\end{tabular}};
  \node[label={0:\{\textsc{Shara}\}}, draw, rounded corners=0.5cm,
      below = 0.5 of dir] (cdd) {\begin{tabular}{c}Clause-Dependent-Disjoint\\ \textsc{co-NP}\end{tabular}};
  \node[label={0:\{\textsc{Ufo}\}},
      below left = 0.5 and 0.5 of cdd] (lin) {\begin{tabular}{c}Linear\\ \textsc{co-NP}\end{tabular}};
  \node[label={180:\{\textsc{Eldarica}\cite{rummer13b}\}},
      below right = 0.5 and 0.5 of cdd] (bd) {\begin{tabular}{c}Body Disjoint\\ \textsc{co-NP}\end{tabular}};
  \node[label={180:\{\textsc{Duality}\cite{bjorner13}\}},
      below = 0.5 of bd] (tree) {\begin{tabular}{c}Tree\\ \textsc{co-NP}\end{tabular}};
\end{scope}
\begin{scope}[every edge/.style={draw=black, very thick}]
  \path[-] (tree) edge (bd);
  \path[-] (bd) edge (cdd);
  \path[-] (lin) edge (cdd);
  \path[-] (cdd) edge (dir);
  \path[-] (dir) edge (rec);
  \path[-] (rec) edge (top);
\end{scope}
\end{tikzpicture}
}

>>>>

% \scalebox{0.75}{%
% }

\begin{tikzpicture}
\tikzstyle{every node}=[draw=black, thin, ellipse]
  \begin{scope}[fill opacity=0.1,text opacity=1]

  \draw node[minimum width=6.2cm,minimum height=6cm,
    label={[anchor=north, inner sep=5pt]north:
      \begin{tabular}{c}Recursion-Free\\\textsc{co-NEXPTIME Complete}\end{tabular}} ]
    at (0,0)
    {};

  \draw node[fill=blue, minimum width=5.5cm,minimum height=4.5cm,
    label={[anchor=south, inner sep=0pt]south:
      \begin{tabular}{c}Directly Solvable\\\textsc{co-NP}\end{tabular}} ]
    at (0,-6mm)
    {};

  \draw node[fill=yellow, minimum width=5cm,minimum height=3cm,
    label={[anchor=north, inner sep=5pt]north:CDD}]
    at (0,-1mm)
    {};

  \draw node[fill=red, minimum width=2.7cm,minimum height=2cm]
    at (10mm,-2mm)
    {\begin{tabular}{c}Body\\Disjoint\end{tabular}};

  \draw node[fill=green, minimum width=2.7cm,minimum height=2cm]
    at (-10mm,-2mm)
    {Linear};

    % \begin{tabular}{c}Directly Solvable\\\textsc{co-NP}\end{tabular}} ]
  \end{scope}
\end{tikzpicture}
